%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}



\addtolength{\oddsidemargin}{-0.65in}
\addtolength{\textwidth}{1.25in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1.55in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\linkicon}{\raisebox{-0.1em}{\faLink}}

\newcommand{\clickable}[2]{%
  \href{#1}{#2\ \linkicon}%
}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING----------
\begin{center}
    {\Huge \scshape Aneesh Grover} \\ \vspace{1pt}
    \href{mailto:agrover@rockets.utoledo.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{agrover@rockets.utoledo.edu}} ~ 
    \href{https://www.linkedin.com/in/aneesh-grover/}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}} ~
    \href{https://github.com/Aneesh-382005}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} ~
    \href{https://www.aneeshgrover.me/}{\raisebox{-0.2\height}\faGlobe\ \underline{Website}}
\end{center}




%-----------EXPERIENCE-----------

\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
    {\clickable{https://timetable.acmthapar.in/}{AcademicAlly}}{July 2024 -- August 2025}
    {Founding Developer -- ACM Thapar Society}{{\hfill\small\textcolor{Gray}{\textbf{React, Python, Pandas, Openpyxl, BeautifulSoup}}}}
    \resumeItemListStart
        \resumeItem{\textbf{Served 10,000+ students} by developing a responsive timetable portal for fast, reliable class schedule lookup.}
        \resumeItem{Built ETL pipelines to transform and validate \textbf{50,000+ Excel rows} into optimized JSON datasets, implementing custom error handling that reduced parsing failures by \textbf{95\%}.}
        \resumeItem{Supported deployment and maintenance of the \textbf{\href{https://timetable.acmthapar.in/}{live portal}}, coordinating with team members.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------PROJECTS-----------


\section{Projects}
\resumeSubHeadingListStart


\resumeProjectHeading
  {\textbf{\clickable{https://github.com/Focus-Board}{FocusBoard - Whiteboard Task Capture System}}}
  {\hfill\small\textcolor{Gray}{Kotlin, FastAPI, CRAFT, TrOCR, Phi-3 Mini, TFLite}}
\resumeItemListStart
  \resumeItem{Built the Android app in Kotlin with ML Kit document scanning and an experimental \textbf{on-device YOLOv26n/TFLite} whiteboard detector, chosen for mobile size constraints.}
  \resumeItem{Engineered a \textbf{3-stage OCR pipeline} using CRAFT for line segmentation, TrOCR for transcription, and Phi-3 Mini for structured calendar JSON generation from handwritten input.}
  \resumeItem{Designed per-device request queues to serialize uploads, preventing concurrent TrOCR worker spawning and \textbf{eliminating cross-device race conditions} under simultaneous load.}
  \resumeItem{Returned structured JSON to the app for user approval before committing tasks to the shared E Ink display.}
\resumeItemListEnd


\resumeProjectHeading
  {\textbf{\clickable{https://github.com/Aneesh-382005/campus-compute}{Campus-Compute - Distributed Compute Framework}}}
  {\hfill\small\textcolor{Gray}{Python, FastAPI, WebSockets, Docker}}
\resumeItemListStart
  \resumeItem{Architected a LAN-distributed compute system with a centralized coordinator and worker nodes, enabling automatic discovery and reconnect handling.}
  \resumeItem{Designed a capability-aware scheduler using CPU, RAM, and GPU metadata to optimize task placement across nodes.}
  \resumeItem{Built a real-time WebSocket dashboard for cluster telemetry, job orchestration, and containerized workload execution.}
\resumeItemListEnd



\resumeProjectHeading
  {\textbf{\clickable{https://mcp.aneeshgrover.me/}{folio.mcp - Personal MCP Server}}}
  {\hfill\small\textcolor{Gray}{TypeScript, Cloudflare Workers, Hono, MCP SDK}}
\resumeItemListStart
  \resumeItem{Built a remote MCP server on Cloudflare Workers exposing GitHub activity, portfolio data, and an LLM-invocable contact tool.}
  \resumeItem{Added a KV layer for GitHub response caching with TTLs and IP-based rate limiting on the contact tool to prevent abuse.}
  \resumeItem{A simple companion frontend at \textbf{\clickable{https://mcp.aneeshgrover.me/}{mcp.aneeshgrover.me}} with dynamic tool discovery; automated deploys via GitHub Actions.}
\resumeItemListEnd


\resumeProjectHeading
  {\textbf{\clickable{https://github.com/kshitiz510/patch-it}{PatchIt - Civic Infrastructure Monitoring}}}%
  {\hfill\small\textcolor{Gray}{PyTorch, YOLO, Depth-Anything-V2}}
\resumeItemListStart
  \resumeItem{Co-led a crowdsourced platform with citizens and contractors to streamline reporting and resolution of road infrastructure issues.}
  \resumeItem{Built a YOLO-based pothole detection pipeline achieving \textbf{85.8\% precision} and \textbf{81.7\% mAP@50}, integrating depth estimation for 3D geometry and repair cost estimation.}
  \resumeItem{Runner-up (Open Innovation) at \textbf{NVIDIA SatHack Hackathon} among 1500+ participants.}
\resumeItemListEnd

\resumeSubHeadingListEnd



%-----------SKILLS-----------


\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages:} Python, Java, C++, JavaScript, TypeScript, SQL \\
    \textbf{Software Engineering \& Systems:} REST APIs, distributed systems, asynchronous processing, WebSockets, system design \\
    \textbf{Machine Learning:} PyTorch, TensorFlow, transformers, vector databases, RAG \\
    \textbf{Infrastructure \& Tools:} Docker, Git, CI/CD, Supabase, OpenCV, CUDA}}
\end{itemize}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
  {University of Toledo}{Toledo, OH}
  {Bachelor of Science in Computer Science and Engineering}{GPA: 3.5/4.0}


\resumeSubHeadingListEnd

%-----------LEADERSHIP & INVOLVEMENT-----------
\section{Leadership \& Involvement}
\resumeSubHeadingListStart

\resumeSubheading
  {Association for Computing Machinery (ACM)}{Nov 2023 -- Present}
  {Executive Board Member \& Machine Learning Bootcamp Lead}{}
  
  \resumeItemListStart
    \resumeItem{Organized Hacklipse 2024, ACM Thapar's flagship hackathon, coordinating operations for \textbf{300+ participants}.}
    \resumeItem{Mentored \textbf{100+ students} through ACM's Machine Learning Bootcamp by designing curriculum and leading weekly technical sessions.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
  \resumeItemListStart
    \resumeItem{ Secured \textbf{runner-up} in \textbf{Open Innovation Category} at \textbf{NVIDIA's SatHack}, competing against \textbf{1500+ participants}.}
    \resumeItem{Awarded Best Use Case for AcademicAlly at ACM Projectathon 2024.}
  \resumeItemListEnd




\end{document}


